Evaluating Informative Hypotheses With Equality and Inequality Constraint: The Bayes Factor Encompassing Prior Approach

### 2021-11-28 Documents/Bookdown/01-case-study.Rmd
update supplemental material

The aim of the study is to compare the different theoretical perspectives regarding the role of mother attachment and father attachment on children's social emotional development. In the literature, four different main theoretical perspectives have been identified [@brethertonFathersAttachmentTheory2010]:

- **Monotropy Theory** - only the mother has an impact on children's development.
- **Hierarchy Theory** - the mother has a greater impact on children development than the  the father.
- **Independence Theory** - all attachment figures are equally important but they affect the children's development differently.
- **Integration Theory** - to understand the impact on children's development it is necessary to consider attachment relationships taken together.

@@

For more information regarding Attachment theory and the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children socio-emotional development, see the main article [TODO: add link article].

@@

To evaluate the different role of father attachment and mother attachment, we consider `r tot_subj()` Italian children from third to sixth school grade. Only middle-childhood children are included in the analysis (`r tot_subj_older()` participants are excluded as older than 12.3 years and `r tot_subj_NA()` participants are excluded are excluded as the age is missing). The total sample size included in the analysis is `r tot_subj_included()` (`r perc_females()` \% Females). Participants frequencies by grade and gender are reported in Table~\@ref(tab:table-gender-grade).

@@

Participants age mean is `r var_info("age_year")`. The participants age summary statistics are reported below and the distribution is presented in Figure~\@ref(fig:plot-age).

@@

Attachment towards the mother and the father was measured separately using the brief Experiences in Close Relationships Scale (ECR; [TODO add references]) completed by the children. Four main attachment styles have been recognized in the literature according to thee levels of *anxiety* and *avoidance*:

@@

To identify children attachment styles towards the mother and towards the father, we conduct two separate cluster analyses. Clusters are obtained using the function `hclust()` (with argument `method="ward.D"`) considering *Euclidean* distances between participants responses to the ECR items.

@@

These results reflect the traditional definition of the four attachment styles. Moreover, attachment styles frequencies are in lines with general results in the literature [TODO: add reference values].

@@

To evaluate if 4 cluster is an appropriate choice, we compare the BIC values of different model-based clustering options. To do that we use the function `mclustBIC()` from the `mclust` R-package [@scruccaMclustClusteringClassification2016]. BIC values of the best three model-based clustering are reported below and overall results are presented in Figure~\@ref(fig:plot-mclust-mother). See `?mclustBIC()` help page for further information.

@@

Results indicate the possible presence of a larger number of clusters. However, considering only 4 clusters seems to us the most reasonable choice. This is in line with attachment theory and general results in the literature. The important thing is hat no smaller number of clusters provided better results than the division in 4 clusters.

@@

These results are no as good as in the mother attachment classification, but they are still reasonable. Moreover, attachment styles frequencies are close to the general results in the literature [TODO: add reference values].

@@

To evaluate if 4 cluster is an appropriate choice, we compare the BIC values of different model-based clustering options as before.  BIC values of the best three model-based clustering are reported below and overall results are presented in Figure~\@ref(fig:plot-mclust-father).

@@

We can observe how values on the diagonal (same attachment styles towards both parents) tends to be larger than others.

@@

Children's social-emotional development was measured using the Strength \& Difficulties Questionnaire (SDQ; [TODO add references]) completed by the teachers. Separate scores for externalizing and internalizing problems were obtained as sum of the questionnaire items.

@@

Participants externalizing problems mean is `r var_info("externalizing_sum")`. The participants externalizing problems summary statistics are reported below and the distribution is presented in Figure~\@ref(fig:plot-externalizing-dist).

@@

Overall, externalizing problems are low. This is expected as the sample is not a clinical sample. Externalizing problems according to attachment styles are reported in Table~\@ref(tab:table-cluster-ext).

@@

Overall, internalizing problems are low. Again, this is expected as the sample is not a clinical sample. Internalizing problems according to attachment styles are reported in Table~\ref(tab:table-cluster-ext).

>>>>

The study aims to compare the different theoretical perspectives regarding the role of mother attachment and father attachment on children's social-emotional development. In the literature, four different main theoretical perspectives have been identified [@brethertonFathersAttachmentTheory2010]:

- **Monotropy Theory** - only the mother has an impact on children's development.
- **Hierarchy Theory** - the mother has a greater impact on children's development than the father.
- **Independence Theory** - all attachment figures are equally important but they affect the children's development differently.
- **Integration Theory** - to understand the impact on children's development it is necessary to consider attachment relationships taken together.

@@

For more information regarding Attachment theory and the formalization of theoretical perspectives regarding the role of mother attachment and father attachment on children's socio-emotional development, see the main article [TODO: add link article].

@@

To evaluate the different roles of father attachment and mother attachment, we consider `r tot_subj()` Italian children from third to sixth school grade. Only middle-childhood children are included in the analysis (`r tot_subj_older()` participants are excluded as older than 12.3 years and `r tot_subj_NA()` participants are excluded as the age is missing). The total sample size included in the analysis is `r tot_subj_included()` (`r perc_females()` \% Females). Participants' frequencies by grade and gender are reported in Table~\@ref(tab:table-gender-grade).

@@

Participants' age mean is `r var_info("age_year")`. The participants’ age summary statistics are reported below and the distribution is presented in Figure~\@ref(fig:plot-age).

@@

Attachment towards the mother and the father was measured separately using the brief Experiences in Close Relationships Scale - Revised Child Version [ECR-RC, @Brenning2014ThePQ; marciBriefExperiencesClose2019] completed by the children. Four main attachment styles have been recognized in the literature according to thee levels of *anxiety* and *avoidance*:

@@

To identify children's attachment styles towards the mother and towards the father, we conduct two separate cluster analyses. Clusters are obtained using the function `hclust()` (with argument `method="ward.D"`) considering *Euclidean* distances between participants responses to the ECR items.

@@

These results reflect the traditional definition of the four attachment styles.

@@

To evaluate if 4 clusters is an appropriate choice, we compare the BIC values of different model-based clustering options. To do that we use the function `mclustBIC()` from the `mclust` R-package [@scruccaMclustClusteringClassification2016]. BIC values of the best three model-based clusterings are reported below and overall results are presented in Figure~\@ref(fig:plot-mclust-mother). See `?mclustBIC()` help page for further information.

@@

Results indicate the possible presence of a larger number of clusters. However, considering only 4 clusters seems to us the most reasonable choice. This is in line with attachment theory and general results in the literature. The important thing is that no smaller number of clusters provided better results than the division in 4 clusters.

@@

These results are not as good as in the mother attachment classification, but they are still reasonable.

@@

To evaluate if 4 clusters is an appropriate choice, we compare the BIC values of different model-based clustering options as before.  BIC values of the best three model-based clusterings are reported below and overall results are presented in Figure~\@ref(fig:plot-mclust-father).

@@

We can observe how values on the diagonal (same attachment styles towards both parents) tend to be larger than others.

@@

Children's social-emotional development was measured using the Strength and Difficulties Questionnaire [SDQ, @goodmanWhenUseBroader2010] completed by the teachers. Separate scores for externalizing and internalizing problems were obtained as the sum of the questionnaire items.

@@

Participants externalizing problems mean is `r var_info("externalizing_sum")`. The participants' externalizing problems summary statistics are reported below and the distribution is presented in Figure~\@ref(fig:plot-externalizing-dist).

@@

Overall, externalizing problems are low. This is expected as the sample is not clinical. Externalizing problems according to attachment styles are reported in Table~\@ref(tab:table-cluster-ext).

@@

Overall, internalizing problems are low. Again, this is expected as the sample is not clinical. Internalizing problems according to attachment styles are reported in Table~\ref(tab:table-cluster-ext).

### 2021-11-28 Documents/Bookdown/02-ext-model-choice.Rmd
update supplemental material

In this chapter, we discuss the appropriate models family to to take into account data characteristics.

@@

Externalizing problems are computed as the sum of 10 items of the SDQ, obtaining discrete scores that range from 0 to 20. Thus, we should use appropriate discrete distribution such as the *Poisson* distribution or the *Negative Binomial*. In the Poisson distribution mean and variance are defined according to the same parameter $\lambda$. On the contrary, Negative Binomial has an extra parameter to adjust the variance allowing more flexibility. Considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe that data have high dispersion with a long right tail. In this case, Poisson distribution would be a poor choice and we prefer Negative Binomial instead.

Again, considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe an high peak of values at zero. Remember that this is not a clinical sample, thus it is expected that children majority has no problems or really few problem. We could question ourselves, however, whether a *Zero-Inflated* model may be appropriate

@@

To evaluate the presence of zero inflation in our data, we compare the number of observed zeros and expected zeros in a Negative Binomial mixed effects model. We consider in the model the role of gender and the interaction between mother attachment and father attachment. Moreover, we consider the children's classroom ID as a random effect to account for teachers' different ability to evaluate children's problems. Using R formula syntax, we have
```{r echo = TRUE, eval=FALSE}
# model formula
externalizing_sum ~ gender + mother * father + (1|ID_class)
```

@@

Results indicate that the model is slightly under-fitting the number of zeros. Now, we can try to fit a *Zero Inflated Negative Binomial* (ZINB) model and compare the performance of the two models. ZINB models are defined as
$$
y_{ij} \sim ZINB(p_{ij}, \mu_{ij}, \phi),
$$
where $p_{ij}$ is the probability of an observation $y_{ij}$ being an extra zero (i.e., a zero not coming from the Negative Binomial distribution) and $1-p_{ij}$ indicates the probability of a given observation $y_{ij}$ being generated form a Negative Binomial distribution with mean $\mu_{ij}$ and variance $\sigma_{ij}^2 = \mu_{ij} + \frac{\mu_{ij}^2}{\phi}$. Moreover, we have that
$$
p_{ij} = \text{logit}^{-1}(X_i^T\beta_p+ Z_j^Tu_p),\\
\mu_{ij} = \text{exp}(X_i^T\beta_{\mu}+ Z_j^Tu_{\mu}).
$$
That is, both $p$ and $\mu$ are modelled separately according to (possibly) different variables. In our case, we consider only the role of gender for $p$ (i.e., the probability of having externalizing problems depends on gender), whereas for $\mu$ the consider also the interaction between mother attachment and father attachment. In both cases, we consider the children's classroom ID as a random effect (teachers may differ in the ability to detect children's problems and quantify them). Using R formula syntax, we have
```{r echo = TRUE, eval=FALSE}
# formula for p
p ~ gender + (1|ID_class)

@@

The ZINB model is fitted using the function `zeroinfl()` from the `pscl` R-package [@zeileisRegressionModelsCount2008]. To compare the ZINB model and the Negative Binomial model we conduct an analysis of *Deviance*. Note that, in the case of generalized linear models (GLM), the deviance is the corresponding of the residual variance used in the traditional ANOVA in the case of linear models.
```{r echo=TRUE, cache=TRUE}
anova(fit_ext_nb, fit_ext_zinb)
```

>>>>

In this chapter, we discuss the appropriate models’ family to take into account data characteristics.

@@

Externalizing problems are computed as the sum of 10 items of the SDQ, obtaining discrete scores that range from 0 to 20. Thus, we should use appropriate discrete distribution such as the *Poisson* distribution or the *Negative Binomial*. In the Poisson distribution mean and variance are defined according to the same parameter $\lambda$. On the contrary, Negative Binomial has an extra parameter to adjust the variance allowing more flexibility. Considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe that data have high dispersion with a long right tail. In this case, the Poisson distribution would be a poor choice and we prefer Negative Binomial instead.

Again, considering data distribution (see Figure~\@ref(fig:plot-externalizing-dist)), we can observe a high peak of values at zero. Remember that this is not a clinical sample, thus it is expected that the majority of children have no problems or really few problems. We could question ourselves, however, whether a *Zero-Inflated* model may be appropriate

@@

To evaluate the presence of zero inflation in our data, we compare the number of observed zeros and expected zeros in a Negative Binomial mixed-effects model. We consider in the model the role of gender and the interaction between mother attachment and father attachment. Moreover, we consider the children's classroom ID as a random effect to account for teachers' different ability to evaluate children's problems. Using R formula syntax, we have
```{r echo = TRUE, eval=FALSE}
# model formula
externalizing_sum ~ gender + mother * father + (1|ID_class)
```

@@

Results indicate that the model is slightly under-fitting the number of zeros. Now, we can try to fit a *Zero Inflated Negative Binomial* (ZINB) model and compare the performance of the two models. ZINB models are defined as
$$
y_{ij} \sim ZINB(p_{ij}, \mu_{ij}, \phi),
$$
where $p_{ij}$ is the probability of an observation $y_{ij}$ being an extra zero (i.e., a zero not coming from the Negative Binomial distribution) and $1-p_{ij}$ indicates the probability of a given observation $y_{ij}$ being generated form a Negative Binomial distribution with mean $\mu_{ij}$ and variance $\sigma_{ij}^2 = \mu_{ij} + \frac{\mu_{ij}^2}{\phi}$. Moreover, we have that
$$
p_{ij} = \text{logit}^{-1}(X_i^T\beta_p+ Z_j^Tu_p),\\
\mu_{ij} = \text{exp}(X_i^T\beta_{\mu}+ Z_j^Tu_{\mu}).
$$
That is, both $p$ and $\mu$ are modelled separately according to (possibly) different variables. In our case, we consider only the role of gender for $p$ (i.e., the probability of having externalizing problems depends on gender), whereas for $\mu$ we also consider the interaction between mother attachment and father attachment. In both cases, we consider the children's classroom ID as a random effect (teachers may differ in the ability to detect children's problems and quantify them). Using R formula syntax, we have
```{r echo = TRUE, eval=FALSE}
# formula for p
p ~ gender + (1|ID_class)

@@

The ZINB model is fitted using the function `glmmTMB()`. To compare the ZINB model and the Negative Binomial model we conduct an analysis of *Deviance*. Note that, in the case of generalized linear models (GLM), the deviance is the corresponding of the residual variance used in the traditional ANOVA in the case of linear models.
```{r echo=TRUE, cache=TRUE}
anova(fit_ext_nb, fit_ext_zinb)
```

### 2021-11-28 Documents/Bookdown/04-ext-model-comparison.Rmd
update supplemental material

To interpret these results, note that, AIC tends to select more complex models that can better explain the data, on the contrary, BIC penalizes complex models to a greater extent.  As pointed by @kuhaAICBICComparisons2004, using the two criteria together is always advocated as agreement provides reassurance on the robustness of the results and disagreement still provides useful information for the discussion. We can say that there is evidence in favour of the role of mother attachment but probably this effect is small.

@@

Considering model `fit_ext_mother`, we can run an analysis of deviance to evaluate the significance of the predictors.
```{r, echo =TRUE, cache=TRUE}
car::Anova(fit_ext_mother)
```
Results confirm a statistically significant effect of gender and mother attachment. The model summary is reported below.
```{r, echo =TRUE, cache=TRUE}
summary(fit_ext_mother)
```
To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-comparison-effects-ext). Not that the marginal predicted values for gender are averaged over mother attachment. Whereas, the marginal predicted values for mother attachment are averaged over gender.
```{r plot-comparison-effects-ext, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment ($n_{subj} = 847$)."}
get_plot_zinb(model = fit_ext_mother, attachment = "mother")
```

>>>>

To interpret these results, note that, AIC tends to select more complex models that can better explain the data, on the contrary, BIC penalizes complex models to a greater extent.  As pointed out by @kuhaAICBICComparisons2004, using the two criteria together is always advocated as agreement provides reassurance on the robustness of the results and disagreement still provides useful information for the discussion. We can say that there is evidence in favour of the role of mother attachment but probably this effect is small.

@@

Considering the model `fit_ext_mother`, we can run an analysis of deviance to evaluate the significance of the predictors.
```{r, echo =TRUE, cache=TRUE}
car::Anova(fit_ext_mother)
```
Results confirm a statistically significant effect of gender and mother attachment. The model summary is reported below.
```{r, echo =TRUE, cache=TRUE}
summary(fit_ext_mother)
```
To evaluate the effect of gender and mother attachment, the marginal predicted values according to gender and mother attachment are presented separately in Figure~\@ref(fig:plot-comparison-effects-ext). Not that the marginal predicted values for gender are averaged over mother attachment. Whereas, the marginal predicted values for mother attachment are averaged over gender.
```{r plot-comparison-effects-ext, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to gender and mother attachment ($n_{subj} = 847$)."}
get_plot_zinb(model = fit_ext_mother, attachment = "mother")
```

### 2021-11-28 Documents/Bookdown/05-ext-BF.Rmd
update supplemental material

To properly evaluate hypotheses with information regarding the expected direction of the effects, we use the Bayes Factor with encompassing prior approach. See the main article for a detailed introduction to this approach [TODO: add link article].

First, we define the encompassing model. Subsequently, we obtain the hypotheses matrices according to the informative hypotheses. Next, we compute the Bayes Factor and, finally, we describe the selected model.

@@

### Prior Choiche

@@

We can evaluate the consequences of different values choice considering the resulting prior predictions. To facilitate this step, we compute prior prediction considering only the intercept and a single parameter of interest. Remembering that the inverse link function (i.e., function that in a GLM transform the model linear prediction into the value on the original response scale) is the exponential function, we consider as intercept the value 1 because $exp(1) \approx 2.7$ that is close to the externalizing problems sample mean  `r ext_mean()`. In Table~\@ref(tab:table-prior-predict), summary information about prior predictions for different standard deviation values is reported.
```{r table-prior-predict}
get_table_prior_predict(format = params$format)
```

Considering that externalizing problems are bounded between 0 and 20, a reasonable prior is  $\mathcal{N}(0,3)$. as prior predicted values cover all possible values without including excessively large values. More diffuse priors would result in values with a higher order of magnitude and tighter priors would exclude plausible values. The influence of prior specification will be subsequently evaluated in a prior sensitivity analysis.

@@

Here we present the obtained hypothesis matrices were on the columns we have the parameters of the encompassing model (excluding the intercept) and each row express an equality constraint or an inequality constraint. Matrices row names follow this notation: names without square brackets indicate a constraint directly on the model parameter; names within square brackets indicate a group condition (that could be the resulting composition of more parameters). For example, `"M_Avoidant:F_Anxious"` indicates the actual interaction term of the model, whereas `"[M_Avoidant_F_Anxious]"` indicate the group condition. This is done because when assuming no interaction or no father attachment effect we set constraints directly on the model parameters, instead, when constraints involve group comparisons, we need to obtain the resulting conditions. Equality and inequality constraints are presented separately.

@@

- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero). There are no inequality constraints.

@@

- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
```{r cache=TRUE}
get_hypothesis_matrix("monotropy", encompassing_model_ext)$ineq
```

@@

- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
```{r cache=TRUE}
get_hypothesis_matrix("hierarchy", encompassing_model_ext)$ineq
```

@@

- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
```{r cache=TRUE}
get_hypothesis_matrix("independence", encompassing_model_ext)$ineq
```

@@

- **Inequality matrix**, $R_{iI} > 0$ (each row is set to grater than zero).
```{r cache=TRUE}
get_hypothesis_matrix("integration", encompassing_model_ext)$ineq
```

@@

This adjustment, however, requires the hypothesis matrix $R$ to be *full-row-rank* (i.e., all constraints are linearly independent). However, this is not the case of the Hierarchy Hypothesis. To overcome this issue, we follow the solution presented in the main article. First, define $R^*$ selecting the maximum number of independent rows. In this case, 15 contrast are independent

@@

Before computing the Bayes Factor, note that we have a set of comparable hypotheses as exists a common solution to the set of linear equations obtained by setting all hypothesis constraints equal to zero. The solution is the trivial solution of simply consider all parameters equal to zero. Finally, we do not need to standardize our parameters as they represent mean groups differences. See the main article for a detailed explanation [TODO: add link article].

@@

To compute the Bayes Factor we evaluate marginal densities and conditional probabilities as described in detail in the main article [TODO: add link article]. Bayes Factor and posterior probability of each hypothesis are reported in Table~\@ref(tab:table-bf-results-ext).

@@

Remember, however, that prior specification affects the Bayes Factor results. Therefore, we also evaluate the results considering different prior settings. In particular, we consider as possible priors for the parameters of interest:

@@

Overall results consistently indicate the Monotropy Hypothesis as the most supported by the data. However, we can observe two distinct patterns. As the prior gets more diffuse, the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases. Moreover, the probability of the Null Hypothesis increases with more diffuse prior, whereas the probabilities of the Hierarchy, Independence and Integration Hypothesis increases with tighter priors.

To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point. On the contrary, equality constraints are highly affected by the prior definition (see the main article for more details[TODO: add link article]).

All the defined hypotheses include equality constraints. Thus, for more diffuse prior we observe that the order of magnitude of the Bayes Factor comparing each hypothesis with the encompassing model increases. Moreover, the hypothesis with a higher number of equality constraints (e.g., Null Hypothesis) will be favoured over hypotheses with a smaller number of equality constraints (e.g., Hierarchy, Independence and Integration Hypothesis).

@@

One of the limits of the Bayes Factor with the encompassing prior approach is that we only get the selected hypothesis but we do not obtain the actual estimates of the parameters posterior. To overcome this limit we rely on Bayesian inference that allows us to effectively estimate the model parameter posteriors.

@@

To evaluate the fit of the model to the data, we computed the *Bayesian* $R^2$ and using the function `brms::bayes_R2()`, and we present Posterior Predictions in Figure~\@ref(fig:plot-ppcheck-ext).

@@

We can see that the actual variance explained by fixed effects and random effect is around 15\%. Moreover, posterior predictive check indicates a good fit to the data.

>>>>

To properly evaluate hypotheses with information regarding the expected direction of the effects, we use the Bayes factor with the encompassing prior approach. See the main article for a detailed introduction to this approach [TODO: add link article].

First, we define the encompassing model. Subsequently, we obtain the hypotheses matrices according to the informative hypotheses. Next, we compute the Bayes factor and, finally, we describe the selected model.

@@

### Prior Choice

@@

We can evaluate the consequences of different values’ choice considering the resulting prior predictions. To facilitate this step, we compute prior prediction considering only the intercept and a single parameter of interest. Remembering that the inverse link function (i.e., function that in a GLM transform the model linear prediction into the value on the original response scale) is the exponential function, we consider as intercept the value 1 because $exp(1) \approx 2.7$ that is close to the externalizing problems sample mean  `r ext_mean()`. In Table~\@ref(tab:table-prior-predict), summary information about prior predictions for different standard deviation values is reported.
```{r table-prior-predict}
get_table_prior_predict(format = params$format)
```

Considering that externalizing problems are bounded between 0 and 20, a reasonable prior is  $\mathcal{N}(0,3)$. With these settings, prior predicted values cover all possible values without including excessively large values. More diffuse priors would result in values with a higher order of magnitude and tighter priors would exclude plausible values. The influence of prior specification will be subsequently evaluated in a prior sensitivity analysis.

@@

Here we present the obtained hypothesis matrices where on the columns we have the parameters of the encompassing model (excluding the intercept) and each row expresses an equality constraint or an inequality constraint. Matrices’ row names follow this notation: names without square brackets indicate a constraint directly on the model parameter; names within square brackets indicate a group condition (that could be the resulting composition of more parameters). For example, `"M_Avoidant:F_Anxious"` indicates the actual interaction term of the model, whereas `"[M_Avoidant_F_Anxious]"` indicates the group condition. This is done because when assuming no interaction or no father attachment effect we set constraints directly on the model parameters, instead, when constraints involve group comparisons, we need to obtain the resulting conditions. Equality and inequality constraints are presented separately.

@@

- **Inequality matrix**, $R_{iI} > 0$ (each row is set greater than zero). There are no inequality constraints.

@@

- **Inequality matrix**, $R_{iI} > 0$ (each row is set greater than zero).
```{r cache=TRUE}
get_hypothesis_matrix("monotropy", encompassing_model_ext)$ineq
```

@@

- **Inequality matrix**, $R_{iI} > 0$ (each row is set greater than zero).
```{r cache=TRUE}
get_hypothesis_matrix("hierarchy", encompassing_model_ext)$ineq
```

@@

- **Inequality matrix**, $R_{iI} > 0$ (each row is set greater than zero).
```{r cache=TRUE}
get_hypothesis_matrix("independence", encompassing_model_ext)$ineq
```

@@

- **Inequality matrix**, $R_{iI} > 0$ (each row is set greater than zero).
```{r cache=TRUE}
get_hypothesis_matrix("integration", encompassing_model_ext)$ineq
```

@@

This adjustment, however, requires the hypothesis matrix $R$ to be *full-row-rank* (i.e., all constraints are linearly independent). However, this is not the case with the Hierarchy Hypothesis. To overcome this issue, we follow the solution presented in the main article. First, define $R^*$ selecting the maximum number of independent rows. In this case, 15 contrast are independent

@@

Before computing the Bayes factor, note that we have a set of comparable hypotheses as it exists a common solution to the set of linear equations obtained by setting all hypothesis constraints equal to zero. The solution is the trivial solution of simply considering all parameters equal to zero. Finally, we do not need to standardize our parameters as they represent mean groups’ differences. See the main article for a detailed explanation [TODO: add link article].

@@

To compute the Bayes factor we evaluate marginal densities and conditional probabilities as described in detail in the main article [TODO: add link article]. Bayes factor and posterior probability of each hypothesis are reported in Table~\@ref(tab:table-bf-results-ext).

@@

Remember, however, that prior specification affects the Bayes factor results. Therefore, we also evaluate the results considering different prior settings. In particular, we consider as possible priors for the parameters of interest:

@@

Overall results consistently indicate the Monotropy Hypothesis as the most supported by the data. However, we can observe two distinct patterns. As the prior gets more diffuse, the order of magnitude of the Bayes factor comparing each hypothesis with the encompassing model increases. Moreover, the probability of the Null Hypothesis increases with more diffuse prior, whereas the probabilities of the Hierarchy, Independence and Integration Hypothesis increases with tighter priors.

To interpret these patterns, remember that order constraints are insensitive to the distribution specification as long as the distribution is symmetric and centred on the constraint focal point. On the contrary, equality constraints are highly affected by the prior definition (see the main article for more details [TODO: add link article]).

All the defined hypotheses include equality constraints. Thus, for more diffuse prior we observe that the order of magnitude of the Bayes factor comparing each hypothesis with the encompassing model increases. Moreover, the hypothesis with a higher number of equality constraints (e.g., Null Hypothesis) will be favoured over hypotheses with a smaller number of equality constraints (e.g., Hierarchy, Independence and Integration Hypothesis).

@@

One of the limits of the Bayes factor with the encompassing prior approach is that we only get the selected hypothesis but we do not obtain the actual estimates of the parameters posterior. To overcome this limit we rely on Bayesian inference that allows us to effectively estimate the model parameter posteriors.

@@

To evaluate the fit of the model to the data, we computed the *Bayesian* $R^2$, using the function `brms::bayes_R2()`, and we present Posterior Predictions in Figure~\@ref(fig:plot-ppcheck-ext).

@@

We can see that the actual variance explained by fixed effects and random effects is around 15\%. Moreover, the posterior predictive check indicates a good fit to the data.

### 2021-11-28 Documents/Bookdown/06-ext-conclusion.Rmd
add bookdown int analysis
update supplemental material

---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Conclusions Externalizing Problems {#conclusion-ext}

Overall, we obtained consistent results from the three different approaches. Males have more problems than Females and, regarding attachment, only mother attachment influence children's externalizing problems. In particular, we observed the following pattern: Secure children have the lowest level of problems, Anxious and Avoidant children have a similar, intermediate, level of problems, and Fearful children have the highest level of problems. Taken together, these results support the Monotropy Theory.

@@

- Considering the NHST approach, we actually only found that it is unlikely that mother attachment has no effect. Thus, we reject the null hypothesis but we can not quantify the evidence in favour of any of our hypotheses. 
- Only model comparison allow us to quantify the relative evidence of our models. Model comparison results clearly indicated evidence in favour of an effect of mother attachment but not father attachment. However, using information criteria we could not directly evaluate our informative hypotheses regarding the expected effects, but only the presence of any effect.
- Bayes Factor with encompassing prior approach allowed us to directly test our informative hypotheses regarding the expected effects. Results clearly selected the Monotropy theory as the most likely theory among those considered.

>>>>

---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Conclusions {#conclusion-ext}

Overall, we obtained consistent results from the three different approaches. Males have more problems than Females and, regarding attachment, only mother attachment influences children's externalizing problems. In particular, we observed the following pattern: Secure children have the lowest level of problems, Anxious and Avoidant children have a similar, intermediate, level of problems, and Fearful children have the highest level of problems. Taken together, these results support the Monotropy Theory.

@@

- Considering the NHST approach, we actually only found that it is unlikely that mother attachment has no effect. Thus, we reject the null hypothesis but we can not quantify the evidence in favour of any of our hypotheses. 
- Only model comparison allows us to quantify the relative evidence of our models. Model comparison results clearly indicated evidence in favour of an effect of mother attachment but not father attachment. However, using information criteria we could not directly evaluate our informative hypotheses regarding the expected effects, but only the presence of any effect.
- Bayes factor with encompassing prior approach allowed us to directly test our informative hypotheses regarding the expected effects. Results clearly selected the Monotropy theory as the most likely theory among those considered.

### 2021-11-28 Documents/Bookdown/07-int-model-choice.Rmd
update supplemental material

As in the case of externalizing problems, we evaluate whether a *Zero-Inflated* model may be appropriate. We compare the number of observed zeros and expected zeros in a Negative Binomial mixed effects model considering the same predictors as in the case of externalizing problems. Using R formula syntax, we have
```{r echo = TRUE, eval=FALSE}
# model formula
internalizing_sum ~ gender + mother * father + (1|ID_class)
```

@@

Overall, results indicate that the ZINB model performs better than the Negative Binomial model. Note, however, that BIC actually prefers the model without zero inflation. Nevertheless, in the following analyses we decide to use ZINB models to be consistent with the externalizing problems analysis.

>>>>

As in the case of externalizing problems, we evaluate whether a *Zero-Inflated* model may be appropriate. We compare the number of observed zeros and expected zeros in a Negative Binomial mixed-effects model considering the same predictors as in the case of externalizing problems. Using R formula syntax, we have
```{r echo = TRUE, eval=FALSE}
# model formula
internalizing_sum ~ gender + mother * father + (1|ID_class)
```

@@

Overall, results indicate that the ZINB model performs better than the Negative Binomial model. Note, however, that BIC actually prefers the model without zero inflation. Nevertheless, in the following analyses, we decide to use ZINB models to be consistent with the analysis of the externalizing problems.

### 2021-11-28 Documents/Bookdown/08-int-nhst.Rmd
update supplemental material

Following the traditional NHST approach, we consider the model previously defined that includes all effects of interest (gender effect and the interaction between mother attachment and father attachment). Results of the analysis of deviance are reported below.
```{r, echo =TRUE, cache=TRUE}
car::Anova(fit_int_zinb)
```
Results indicate only a statistically significant effect of mother attachment. On the contrary, the interaction and father attachment are not significant. The model summary is reported below.
```{r, echo =TRUE, cache=TRUE}
summary(fit_int_zinb)
```
To evaluate the effect of mother attachment, the marginal predicted values are presented in Figure~\@ref(fig:plot-nhst-effects-int). Not that the marginal predicted values are averaged over father attachment and gender effect.
```{r plot-nhst-effects-int, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to mother attachment. Values are averaged over the other effects ($n_{subj} = 847$)."}
get_plot_zinb(model = fit_int_zinb, attachment = "mother", gender = FALSE)
```

@@

After adjusting p-values we actually get that there are no statistically significant differences. Without adjusting, difference between Anxious and Secure children and the difference between Fearful and Secure children have a low (but not statistically significant) *p*-value.
```{r, cache=TRUE, echo = TRUE}
emmeans::contrast(emmeans::emmeans(fit_int_zinb, specs = ~ mother ),
                  "pairwise", adjust = NULL)
```

>>>>

Following the traditional NHST approach, we consider the model previously defined that includes all effects of interest (gender effect and the interaction between mother attachment and father attachment). Results of the analysis of deviance are reported below.
```{r, echo =TRUE, cache=TRUE}
car::Anova(fit_int_zinb)
```
Results indicate only a statistically significant effect of mother attachment. On the contrary, the interaction and father attachment are not significant. The model summary is reported below.
```{r, echo =TRUE, cache=TRUE}
summary(fit_int_zinb)
```
To evaluate the effect of mother attachment, the marginal predicted values are presented in Figure~\@ref(fig:plot-nhst-effects-int). Note that the marginal predicted values are averaged over father attachment and gender effect.
```{r plot-nhst-effects-int, cache=TRUE, fig.asp=.65, message=FALSE, fig.cap="Marginal predicted values according to mother attachment. Values are averaged over the other effects ($n_{subj} = 847$)."}
get_plot_zinb(model = fit_int_zinb, attachment = "mother", gender = FALSE)
```

@@

After adjusting p-values we actually get that there are no statistically significant differences. Without adjusting, the difference between Anxious and Secure children and the difference between Fearful and Secure children have a low (but not statistically significant) *p*-value.
```{r, cache=TRUE, echo = TRUE}
emmeans::contrast(emmeans::emmeans(fit_int_zinb, specs = ~ mother ),
                  "pairwise", adjust = NULL)
```
